\vspace{5cm} \normalsize \textsc{\NetIDb} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{\documenttitle}} \HRule{2pt} \\ [0.5cm] \normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\ }\normalsize \vspace*{5\baselineskip}

### 2025-04-29 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%----------FONT AND GEOMETRY DEFINITION----------%
\usepackage[a4paper, hmargin=3.0cm, vmargin=3.0cm]{geometry}
\voffset = -0.75cm
\usepackage{arev}
\usepackage{helvet}
\renewcommand{\rmdefault}{\sfdefault}
\usepackage[math]{blindtext}
%---------SPACING----------%
\usepackage{setspace}
\setstretch{1.5}

@@

By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings\cite{Cox2InhibitorsReview}, demonstrating \gls{ai}’s potential as a powerful tool in computational chemistry research. Our approach not only validates \gls{ai}’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing \gls{cox2} interactions.Additionaly, this study aims to bridge the gap between \gls{ai} and computational chemistry, reinforcing the \gls{ai}’s potential to revolutionise drug discovery and molecular research. The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process. Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. One of the best drug candidates is the Celecoxib (Def. (\ref{definitionCelecoxib})) and the Rofecoxib (Def. (\ref{definitionRofecoxib})). The the Physical Chemistry Unit at UAB\cite{UAB_ComputationalChemistry}, is experimenting with azophotoswitches as COX-2 inhibitos.

\newpage
\section{Objectives}

\newpage
\section{Methodology}
The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.

The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database. Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Def. \ref{definitionIC50}) with a limit of 1000 entries per request. The process is iterated until all data is extracted leading a total of 7979 molecules. Hence the datasheet is processed in pandas dataframes\cite{PythonPackagePandas} and encrypted into binary feather files to optimise reading-writting speed. By removing entries with the same canonical smiles a total of 5112 molecules remain. Among this entries well known drugs such as Celecoxib (Def. \ref{definitionCelecoxib}), Rofecoxib (Def. \ref{definitionRofecoxib}) or even Ibuprofen can be found. However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure. A hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e. molecules). \par 
With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule. Still, by deleting molecular descriptors with null values 2917 remain. Here, the Pearson correlation coefficient between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors.

At this stage, the average $IC_{50}$ is calculated, and the neighborhood size corresponding to the percentage defined by the hard-coded variable \emph{percentageErased} is removed. This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}, those with lower and higher $IC_{50}$ values, respectively. Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} and a \emph{testing set}, following the proportion specified by the hard-coded variable \emph{testSizeProportion}. This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{GeneralSources/DataSplittingDiagram.pdf}
\caption{Splitting and processing data's scheme.}
\label{FigureDataSplittingDiagram}
\end{figure}
Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others. This algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets. Later, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}.

Using the results, the \emph{True Positive Rate} (Def. \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def. \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def. \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def. \ref{definitionMatthewsCorrelationCoeficient}) are computed. Based on these computational results, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to obtain the best results.

\newpage
\section{Results and Discussion}\label{sectionResultsAndDiscussion}
In Figure (\ref{figureGraphicGbindingIC50}) we present the results bla bla bla the data is stored in appendix \ref{appendixTableOfResults}

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
	\caption{Graphic of the azophotoswitches from appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
	\label{figureGraphicGbindingIC50}
\end{figure}

@@

\section{Table of results}\label{appendixTableOfResults}

\begin{table}[H]
    \centering
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
        Pyrazole & 1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145.893274 \\ \hline
        Pyrazole & 2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160.715075 \\ \hline
        Pyrazole & 3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192.302751 \\ \hline
        Pyrazole & 4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306.280176 \\ \hline
        Pyrazole & 5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238.028688 \\ \hline
        Pyrazole & 6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142.842111 \\ \hline
        Pyrazole & 8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240.476605 \\ \hline
        Pyrazole & 9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171.543375 \\ \hline
        Pyrazole & 10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247.718353 \\ \hline
        Pyrazole & 11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215.242455 \\ \hline
        Pyrazole & 12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196.189309 \\ \hline
        Pyrazole & 13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220.685948 \\ \hline
        Pyrazole & 14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231.70988 \\ \hline
        Pyrazole & 15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235.929591 \\ \hline
        Pyrazole & 16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149.258659 \\ \hline
        Furan & 1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171.3118 \\ \hline
        Furan & 2 & \ch{H} & \ch{H} &  & 0.193 & 189.723234 \\ \hline
        Furan & 3 & \ch{F} & \ch{H} &  & -4.8383 & 133.666586 \\ \hline
        Furan & 4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158.679542 \\ \hline
        Furan & 5 & \ch{Br} & \ch{H} &  & -3.4217 & 144.849203 \\ \hline
        Furan & 6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139.974502 \\ \hline
        Furan & 7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148.510406 \\ \hline
        Furan & 8 & \ch{H} & \ch{F} &  & -6.55 & 122.352426 \\ \hline
        Furan & 9 & \ch{F} & F &  & -0.1311 & 189.013485 \\ \hline
        Furan & 10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127.541229 \\ \hline
        Furan & 11 & \ch{Br} & \ch{F} &  & 6.1474 & 241.164891 
            \end{tabular}
\end{table}

\begin{table}[H]
    \centering
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
        Thiophene & 1 & \ch{F} & \ch{H} &  & 1.2724 & 192.519195 \\ \hline
        Thiophene & 2 & \ch{H} & \ch{F} &  & -2.7842 & 152.750403 \\ \hline
        Thiophene & 3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120.103107 \\ \hline
        Pyrrole & 1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151.424098 \\ \hline
        Pyrrole & 2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164.211081 \\ \hline
        Benzene & 1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168.708238 \\ \hline
        Benzene & 2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208.784609 \\ \hline
        Benzene & 3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232.955871 \\ \hline
        Benzene & 4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155.416193 \\ \hline
        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
        Indole & 3 &  &  &  & -5.532 & 111.153348 \\ \hline
        TwoRings & 2 & \ch{NH} & O & \ch{H} & -2.2146 & 165.648426 \\ \hline
        TwoRings & 3 & O & \ch{NH} & \ch{H} & -0.7334 & 178.354687 \\ \hline
        TwoRings & 6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235.15246 \\ \hline
        TwoRings & 7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77.7978863 \\ \hline
        TwoRings & 8 & O & O & \ch{CH_3} & -3.5413 & 142.268104 
    \end{tabular}
\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
%----------FONT AND GEOMETRY DEFINITION----------%
\usepackage[a4paper, hmargin=3.0cm, vmargin=3.0cm]{geometry}
\voffset = -0.75cm
\usepackage{arev}
\usepackage{helvet}
\renewcommand{\rmdefault}{\sfdefault}
\usepackage[math]{blindtext}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
%---------SPACING----------%
\usepackage{setspace}
\setstretch{1.5}

@@

By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings\cite{Cox2InhibitorsReview}, demonstrating \gls{ai}’s potential as a powerful tool in computational chemistry research. Our approach not only validates \gls{ai}’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing \gls{cox2} interactions. Additionaly, this study aims to bridge the gap between \gls{ai} and computational chemistry, reinforcing the \gls{ai}’s potential to revolutionise drug discovery and molecular research. The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process. Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. Still some alternative therapies related with \gls{nsaid}s are being explored, in particular, one of the most revolutionary ideas is the application of azophotoswitches in drug design.

We define a molecule as an azophotoswitch if it contains an azo bond (\ch{N=N}) that is sensitive to configurational transformations upon photo-excitation. For instance, let us consider the case of (E/Z)-N,1-diphenylmethanimine,
\begin{figure}[H]
\captionsetup{type=scheme}
\centering
\schemestart
\scalebox{0.8}{
	\chemfig[angle increment=30]{*6(-=-(-[1]N=[-1]N-*6(-=-=-=))=-=)}}
	\arrow{<=>[$h\nu$]}
\scalebox{0.8}{
	\chemfig[angle increment=30]{
	N(-[-4]*6(-=-=-=))=[0]N-[-2]*6(-=-=-=)
	}}
\schemestop
	\caption{(E/Z)-N,1-diphenylmethanimine conversion as an example of an azophotoswitch.}
\label{AzophotoswitchExampleFigure}
\end{figure}
The photo-induced E/Z isomerization leads to distinct bioactivities for each configuration. This variation arises from the stereochemical constraints required for a molecule to bind to a target protein. Typically, a protein’s binding site has a specific shape, and only molecules whose conformation matches this shape can interact effectively. In the context of an azophotoswitch, one isomer may fit precisely into the binding pocket, leading to strong interactions, while the other may not. Accordingly, we refer to the isomer that interacts most effectively with the protein as the active configuration, and the other as the inactive configuration.\footnote{In the context of this project, interaction refers to inhibition of the protein’s activity.} \footnote{Generally, the trans-isomer is considered the active configuration, while the cis-isomer is considered inactive. However, exceptions exist.}

The primary application of azophotoswitches in drug design is the administration of the inactive isomer, which is assumed to be non-toxic to the organism. Later, the active configuration is generated through selective photo-excitation at the target site. This strategy minimizes drug activity in unintended tissues, thereby reducing side effects. As a result, higher dosages may be administered safely by localizing the therapeutic effect to the desired area. These therapies are still in the experimental stage and remain primarily within research and development.

Among the most promising drug candidates for \gls{cox2} inhibition are Celecoxib (Definition \ref{definitionCelecoxib}) and Rofecoxib (Definition \ref{definitionRofecoxib}).\footnote{These compounds are often referred to as coxib drugs due to the common suffix -coxib.} At the Physical Chemistry Unit of the UAB \cite{UAB_ComputationalChemistry}, researchers are investigating azophotoswitches as potential COX-2 inhibitors, using molecular structures inspired by Celecoxib. Various computational analyses have been conducted, with particular attention to the binding free energy ($\Delta G_{\text{binding}}$).\footnote{Additional results are provided in Appendix \ref{appendixTableOfResults}.}

As an application of our \gls{ml}-based predictive models, we aim to estimate the \gls{ic50} values of azophotoswitch prototypes.\footnote{These values are predictions, as no experimental or simulated data are currently available.} We will then compare these predictions with the computed $\Delta G_{\text{binding}}$ values, as both metrics are indicative of inhibition efficacy. While a direct linear correlation is not expected, we hypothesize that lower \gls{ic50} values should correspond to lower (more negative) $\Delta G_{\text{binding}}$ values, reflecting stronger binding affinities. These relationships will be explored in detail in Section \ref{sectionResultsAndDiscussion}.

In conclusion, this study seeks to bridge the gap between Artificial Intelligence and computational chemistry, demonstrating AI’s potential to revolutionize drug discovery and molecular research. Accurate predictions of inhibition potential could accelerate the development of new pharmaceuticals, reduce the need for costly laboratory experiments, and streamline the drug screening process. Furthermore, identifying key molecular descriptors linked to inhibition may provide valuable insights into chemical interactions, opening new directions for research in medicinal chemistry and bioinformatics.
\newpage
\section{Objectives}

\newpage
\section{Methodology}\label{sectionMethodology}
The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.

The target protein's ID is set at \emph{CHEMBL230} corresponding to the COX-2 ID in the ChEMBL database. Utilising \emph{requests} python package\cite{PythonPackageRequests} a query URL is sent asking for all molecules with a know $IC_{50}$ value (Def. \ref{definitionIC50}) with a limit of 1000 entries per request. The process is iterated until all data is extracted leading a total of 7979 molecules. Hence the datasheet is processed in pandas dataframes\cite{PythonPackagePandas} and encrypted into binary feather files to optimise reading-writting speed. By removing entries with the same canonical smiles a total of 5112 molecules remain. Among this entries well known drugs such as Celecoxib (Def. \ref{definitionCelecoxib}), Rofecoxib (Def. \ref{definitionRofecoxib}) or even Ibuprofen can be found. However the $IC_{50}$ molecules range is comprehended from $10^{-3}$ to $10^{8}$ nM, a counterproductive range for the AI training procedure. Since we are interested in testing azophotoswitches with presumably low \gls{ic50}, training \gls{ml} models with data of the order of $10^{8}$ or $10^{3}$ nM can be counterproductive since the model might misinterpret the data.\footnote{Typically the range of the azophotoswitches \gls{ic50} is arround the Celecoxib's \gls{ic50}, i.e. arround $120$ nM}. Consecutivelly, a hard-coded range is filtered discarding all molecules outside the given range, for the most part of the analysis this range is set at $[0,200]$ nM \footnote{this $IC_{50}$ working range is the standard in this kind of studies \cite{MachineLearningPaper5Lipoxygenase}.} which reduces the dataset to 1438 entries (i.e. molecules).

With the AlvaDesk-python \cite{AlvaDescSecondPaper} facility, the chemical descriptors (i.e., the chemical fingerprint) of each molecule are computed, providing a total of $5800$ descriptors per molecule. Still, some chemical descriptor need from the presence of a certain atom, for instance a chemical descriptor related to presence of a metal in the molecule, or active gorup, for example chemical descriptor related to the presence of a carboxilic acid, or chemical descriptor related triple bound among other possiblities. The computation of this chemical descriptors appear as \emph{null values}. By deleting molecular descriptors with null values 2917 chemical descriptors remain. Here, the Pearson correlation coefficient (Def. (\ref{definitionPersonCoefficient})) between each chemical descriptor and the $IC_{50}$ value is computed, providing insight into the direct relationship between $IC_{50}$ and the descriptors. This relationship will be discussed in the Results and Discussion Section (\ref{sectionResultsAndDiscussion}).

At this stage, the average $IC_{50}$ is calculated, and the neighborhood size corresponding to the percentage defined by the hard-coded variable \emph{percentageErased} is removed. This allows us to distinguish between \emph{highly active molecules} and \emph{least active molecules}, those with lower and higher $IC_{50}$ values, respectively. By doing so, it is possible to compute the classification accuracy statistics of the model from the cluster association of each prediction. Thus we can compare each prediction of each molecules to experimental data, i.e. the model predicts a molecule to be highly active molecule to a highly active molecule this will be denoted as a \gls{tp}. Similarly we can define a \gls{tn}, \gls{fp} and \gls{fn} . This procedure is an standard for evaluating a \gls{ml} model realiability.

Subsequently, each set of substances is randomly divided into two datasets: a \emph{training set} for training the \gls{rf} algorithm and a \emph{testing set} for testing the statistics and realiability of the \gls{rf} model, following the proportion specified by the hard-coded variable \emph{testSizeProportion}. This procedure is illustrated in Figure (\ref{FigureDataSplittingDiagram}).
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{GeneralSources/DataSplittingDiagram.pdf}
\caption{Splitting and processing data's scheme.}
\label{FigureDataSplittingDiagram}
\end{figure}
Afterward, a Random Forest algorithm is trained using the Sticky Learn \cite{PythonPackageStickitLearn} Python package, which is supported by Microsoft and Google among others. This algorithm generates a large number of random decision trees (determined by the hard-coded variable \emph{numberOfTrees}), which are trained with the training sets. Typically the more trees the model is trained with the best accuracy in the predictions, nevertheless the computational cost for each model training also increases with the number of trees. It is key to remark that the predictions' accuracy can not be arbitrarily improved by only increasing the number of trees of the \gls{rf} model. The predictions' accuracy is bonded to the data the model is trained with, thus if the data does not provide enough information about the insight of the protein, more accurate predictions can not be archived independently of the number of trees of the model. As a general criteria we can affirm that,
\begin{align*}
	\uparrow\text{Data}\quad+\uparrow\text{Number of trees}\implies\uparrow\text{Predictions' accuracy}\\
	\downarrow\text{Data}\quad+\downarrow\text{Number of trees}\implies\downarrow\text{Predictions' accuracy}
\end{align*}
but more data or more number of trees independently will not lead to better accuracy,
\begin{align*}
	\uparrow\text{Number of trees}\nrightarrow\uparrow\text{Predictions' accuracy}\\
	\uparrow\text{Data}\nRightarrow \uparrow\text{Predictions' accuracy}
\end{align*}

Later, these models are evaluated by predicting the $IC_{50}$ values of the \emph{testing sets}. Using the results, the \emph{True Positive Rate} (Def. \ref{definitionTruePositiveRate}), \emph{True Negative Rate} (Def. \ref{definitionTrueNegativeRate}), \emph{Classification Accuracy} (Def. \ref{definitionClassificationAccuracy}), and \emph{Matthews Correlation Coefficient} (Def. \ref{definitionMatthewsCorrelationCoeficient}) are computed. Based on these computational results, the variables \emph{percentageErased}, \emph{testSizeProportion}, and \emph{numberOfTrees} are manually adjusted to obtain the best results.

Finally, the \gls{rf} algorithm with best statistics\footnote{The ruling criteria used to classify one model to have "better statistics" than other is discussed in section (\ref{sectionResultsAndDiscussion})} are used to predict the \gls{ic50} of the azophotoswitch prototipes classified in Appendix (\ref{appendixAzophotoshiches}). This procedure begins with the computation of the chemical descriptors with AlvaDesk software \cite{MauriMolecularDescriptorsBook}, then the pertinent chemical descriptor are erased in order to match the ones th

\newpage
\section{Results and Discussion}\label{sectionResultsAndDiscussion}
\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth, trim={0.85cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/DataGapRepresentationIC50percentageEresed15.0Gap_min_32Gap_max_53.pdf}
	\caption{\gls{ic50} values }
	\label{figureGraphicRecurrecyIC50}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth, trim={0.6cm 0.3cm 1.5cm 1.35cm}, clip]{../Plots/ChEMBL_ExtractorData_CHEMBL230_IC50_1000CorrelationFactors.pdf}
	\caption{Pearson correlation coefficient for each chemical descriptor.}
	\label{figureGraphicCorrelationFactor}
\end{figure}

In Figure (\ref{figureGraphicGbindingIC50}) we present the results for the predicted \gls{ic50} in terms of the $\Delta G_{binding}$ provided by the Physical Chemistry Unit of the UAB. The exact results are stored in Appendix \ref{appendixTableOfResults} in Tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}), additionall the conditions under which the Random Forest (\gls{rf}) algorithm has been trained and the statistics analysis of its predictions is stored in Table (\ref{TableConditionsMainResults}).
\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
	\caption{Graphic of the azophotoswitches from Appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
	\label{figureGraphicGbindingIC50}
\end{figure}

Furthermore, we may also show the statistics and reliability of this results in Table (\ref{TableStatisitcsMainResults}).
\begin{table}[H]
    \centering	
	\caption{Statistics for the computation of the results from tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
	\label{TableStatisitcsMainResults}
	\begin{tabular}{c|c}
		Mean Squared Error       & 1202.70\\\hline
		R-squared                & 0.89\\\hline
		ClassificationAcuracy    & 0.94\\\hline
		MatthewsCorrelationFactor& 0.87
    \end{tabular}
\end{table}

@@

\section{Table of results}\label{appendixTableOfResults}
\begin{table}[H]
    \centering
	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
	\label{TableMainResults1}
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
		Pyrazole & \ref{figureCelecoxibPyrazole}.1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235 \\ \hline
        Pyrazole & \ref{figureCelecoxibPyrazole}.16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.2 & \ch{H} & \ch{H} &  & 0.193 & 189 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.3 & \ch{F} & \ch{H} &  & -4.8383 & 133 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.5 & \ch{Br} & \ch{H} &  & -3.4217 & 144 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.8 & \ch{H} & \ch{F} &  & -6.55 & 122 \\ \hline
        Furan & \ref{figureCelecoxibFuran}.9 & \ch{F} & F &  & -0.1311 & 189\\ \hline
        Furan & \ref{figureCelecoxibFuran}.10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127\\ \hline
        Furan & \ref{figureCelecoxibFuran}.11 & \ch{Br} & \ch{F} &  & 6.1474 & 241
            \end{tabular}
\end{table}

\begin{table}[H]
    \centering	
	\caption{Results for the $\Delta$G$_{binding}$ and \gls{ic50}. The conditions and estatistics under which this computations have been done are stored in Table (\ref{TableConditionsMainResults}).}
	\label{TableMainResults2}
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ (Kcal/mol) & Predicted \gls{ic50} (nM) \\ \hline\hline
        Thiophene & \ref{figureCelecoxibThiophene}.1 & \ch{F} & \ch{H} &  & 1.2724 & 192\\ \hline
        Thiophene & \ref{figureCelecoxibThiophene}.2 & \ch{H} & \ch{F} &  & -2.7842 & 152\\ \hline
        Thiophene & \ref{figureCelecoxibThiophene}.3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120\\ \hline
        Pyrrole & \ref{figureCelecoxibPyrrole}.1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151\\ \hline
        Pyrrole & \ref{figureCelecoxibPyrrole}.2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164\\ \hline
        Benzene & \ref{figureCelecoxibBenzene}.1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168\\\hline
        Benzene & \ref{figureCelecoxibBenzene}.2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208\\ \hline
        Benzene & \ref{figureCelecoxibBenzene}.3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232\\ \hline
        Benzene & \ref{figureCelecoxibBenzene}.4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155\\ \hline
        Indole & \ref{figureCelecoxibIndole}.1 & \ch{H} &  &  & -9.7543 & 74\\ \hline
        Indole & \ref{figureCelecoxibIndole}.2 & \ch{F} &  &  & -6.3397 & 108\\ \hline
        Indole & \ref{figureCelecoxibIndole}.3 &  &  &  & -5.532 & 111\\ \hline
        TwoRings & \ref{figureCelecoxibTwoRings}.2 & \ch{NH} & O & \ch{H} & -2.2146 & 165\\ \hline
        TwoRings & \ref{figureCelecoxibTwoRings}.3 & O & \ch{NH} & \ch{H} & -0.7334 & 178\\ \hline
        TwoRings & \ref{figureCelecoxibTwoRings}.6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235\\ \hline
        TwoRings & \ref{figureCelecoxibTwoRings}.7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77\\ \hline
        TwoRings & \ref{figureCelecoxibTwoRings}.8 & O & O & \ch{CH_3} & -3.5413 & 142
    \end{tabular}
\end{table}

\begin{table}[H]
    \centering	
	\caption{Conditions and statistics for the computation of the results from tables (\ref{TableMainResults1}) and (\ref{TableMainResults2}).}
	\label{TableConditionsMainResults}
	\begin{tabular}{c|c}
		NumberOfTrees            & 250\\\hline
		Erased Percentatge       & 0.0\%\\\hline
		Splitting proportion     & 10.0\% for testing \\\hline
		minimumCorrelationFactor & 0.0\\\hline
		Number of descriptors    & 3040\\\hline
		Mean Squared Error       & 1202.70\\\hline
		R-squared                & 0.89\\\hline
		True Positive            & 994\\\hline
		False Positive           & 8\\\hline
		True Negative            & 1015\\\hline
		False Negative           & 101\\\hline
		True Positive Rate       & 0.91\\\hline
		True Negative Rate       & 0.99\\\hline
		ClassificationAcuracy    & 0.94\\\hline
		MatthewsCorrelationFactor& 0.87
    \end{tabular}
\end{table}
